\sectionheader{Summary}
{
    \itemlist
    {
        \bulletitem{Software engineer with experience of developing web, desktop, service-oriented products and applications based on microservice architecture.}
        \bulletitem{Familiar with well-known practices of building flexible and effective application such as OOD, S.O.L.I.D., DDD, TDD. Understanding of functional paradigm.}
        \bulletitem{Developing specializations:}
        \itemlist
        {
            \bulletitem{.NET stack including Core: WPF, ASP.NET, SignalR, ADO.NET/EF, Dapper, various DI and testing frameworks, PushSharp, Service Stack;}
            \bulletitem{relational and in-memory databases: SQL Server, PostgreSQL, Redis, neo4j, Elasticsearch, MongoDB;}
            \bulletitem{data manipulations with using complex data structures and algorithms;}
            \bulletitem{performance tuning of infrastructure and data access layer code;}
            \bulletitem{support of existing applications/modules written on: ReactJS, Rust, F\#.}
        }
        \bulletitem{Confident in version control systems and effective flows of big project (including distributed teams) development: git, SVN, TFS.}
        \bulletitem{Experience and understanding of high-loaded and/or distributed systems architecture, problems and principles.}
        \bulletitem{Ability to build a simple CI/CD integration, portable development/test environment.}
        \bulletitem{English level: Intermediate.}
        \bulletitem{Familiar with Agile, Kanban development processes.}
    }
}